---
title: ''
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE)

library(pacman)

p_load("tidyverse", "rmarkdown", "ggpubr", "ggspatial", "cowplot", "sjPlot",
       "here","gridExtra","rmapshaper",  "readxl", "plotly", "ggalluvial",
       "MASS", "nlme", "mgcv","data.table", "kableExtra","gtsummary",
       "Hmisc","arsenal","imputeTS","zoo","patchwork", "reactable", "leaflet",
       "rnaturalearth", "sf","tidygeocoder")

orygen_colors <- c(
  "Yes" = "#009E73",             # green
  "No" = "#D55E00",              # red
  "Mixed/Unclear" = "#999999"    # grey
)

```

<style type="text/css">
div.main-container {
  max-width: 1300px !important;
}
</style>


```{r}
dta <- read_excel("WIP Summary table_V3.xlsx")

dta<-dta %>%
  mutate(
    StudySettingGroup = case_when(
      str_detect(`Study setting`, regex("secondary school|classroom|college|university", ignore_case = TRUE)) ~ "Education setting-based",
      str_detect(`Study setting`, regex("clinic|health|counseling|hospital", ignore_case = TRUE)) ~ "Clinic/Health service",
      str_detect(`Study setting`, regex("home|family", ignore_case = TRUE)) ~ "Home-based",
      str_detect(`Study setting`, regex("smartphone|website|app|online|wechat|videoconferencing|text|platform|self-directed|email|phone", ignore_case = TRUE)) ~ "Digital/Online",
      TRUE ~ "Other"
    ),
    DeliveryFormat = case_when(
      str_detect(`Individual or group delivery`, regex("group", ignore_case = TRUE)) ~ "Group-based",
      str_detect(`Individual or group delivery`, regex("individual", ignore_case = TRUE)) ~ "Individual-based",
      TRUE ~ "Unclear"
    )
  )

```


# Map of studies
This map shows where each study in the review was conducted. Click on the pin to see details about the study including how many people took part and what kind of intervention was used. Zoom in to click on each pin.



```{r}
# Optional: keep only needed columns
dta_plot <- dta %>%
  select(`Authors (year of publication)`, Country,  `Number of participants`,`Study setting`, `Program description`)

set.seed(123)
# Geocode countries to lat/lon using tidygeocoder
dta_plot <- dta_plot %>%
  geocode(Country, method = "osm", lat = latitude, long = longitude) %>% 
  mutate(
    lat = jitter(latitude, amount = 5),
    lon = jitter(longitude, amount = 5)
  ) %>% 
  group_by(Country) %>% 
  mutate( n=n(), 
          lat=ifelse(n==1, latitude,lat),
          lon=ifelse(n==1, longitude,lon)) %>% 
  ungroup()


```




```{r,fig.width=12,fig.height=6}

# Create popup text
dta_plot <- dta_plot %>%
  mutate(popup = paste0(
    "<strong>", `Authors (year of publication)`, "</strong><br/>",
    "Country: ", Country, "<br/>",
    "Number of participants: ", `Number of participants`, "<br/>",
    "Study setting: ", `Study setting`, "<br/>",
    "Program description: ", `Program description`
  ))

orygen_icon <- makeIcon(
  iconUrl = "Orygen.png",        # Path to image (ensure it's in working dir or adjust path)
  iconWidth = 30,                # Adjust size as needed
  iconHeight = 30,
  iconAnchorX = 15,              # Anchor in center of icon
  iconAnchorY = 30
)

# Create leaflet map with default markers
m <- leaflet() %>%
  addProviderTiles("CartoDB.Positron")

for (i in seq_len(nrow(dta_plot))) {
  m <- addMarkers(
    map = m,
    lng = dta_plot$lon[i],
    lat = dta_plot$lat[i],
    popup = dta_plot$popup[i],
    icon = orygen_icon
  )
}

m


```




# Study settings 


This figure shows the types of settings where interventions were delivered – including education, digital/online, home-based, clinical/health services, and other settings. The size of each rectangle reflects the number of participants in the study. Hover over each study to see the setting, sample size, and type of program. 



```{r,fig.height=6,fig.width=12}
# Step 1: Prepare data with parent values
plot_dta <- dta %>%
  rename(
    Authors = `Authors (year of publication)`,
    Group = StudySettingGroup,
    N = `Number of participants`,
    Support = `Social support element`
  ) %>%
  mutate(
    N = as.numeric(N),
    Support = str_wrap(Support, 30)
  )

# Step 2: Create top-level nodes
top_nodes <- plot_dta %>%
  group_by(Group) %>%
  summarise(N = sum(N), .groups = "drop") %>%
  mutate(
    Authors = Group,
    Group = "",  # root
    Support = NA_character_
  )

# Step 3: Combine study-level and top-level rows
treemap_data <- bind_rows(plot_dta, top_nodes)

# Step 4: Define group colors
group_colors <- c(
  "Clinic/Health service"     = "#1E3510",
  "Digital/Online"            = "#6D7C64",
  "Education setting-based"   = "#9AA493",
  "Home-based"                = "#D2D7CF",
  "Other"                     = "#F4F5F3"
)

# Step 5: Add color and formatted hover text inside mutate
treemap_data <- treemap_data %>%
  mutate(
    group_label = ifelse(Group == "", Authors, Group),
    color = group_colors[group_label],
    hover_text = paste0(
      "<b>", Authors, "</b><br>",
      "Setting: ", ifelse(Group == "", "Top-level", group_label), "<br>",
      "Sample size: ", N, "<br>",
      "Support: <br>", ifelse(is.na(Support), "Not reported", str_replace_all(Support, "\\n", "<br>"))
    )
  )

# Step 6: Plot with HTML-formatted text hover
plot_ly(
  data = treemap_data,
  type = "treemap",
  labels = ~Authors,
  parents = ~Group,
  values = ~N,
  branchvalues = "total",
  textinfo = "label",
  text = ~hover_text,
  hoverinfo = "text",
  marker = list(colors = treemap_data$color)
)


```







# Characteristics of studies 


This table summarises key details from each study included in the review. Use the boxes in the second row to search for specific characteristics.

```{r}
dta <- read_excel("WIP Summary table_V3.xlsx")
reactable(dta,
  searchable = TRUE,
  filterable = TRUE,
  highlight = TRUE,
  striped = TRUE,
  bordered = TRUE,
  resizable = TRUE,
  defaultPageSize = 10)
```



